Transforming Trash as an Artistic Act

### 2016-01-17 drafts/chapter2.tex
Relocation, turnitin fixes
Former-commit-id: e8de078896595446f38348c7c970a0b9f22fae30

In this chapter trash and the practice of transforming trash is examined in theoretical and conceptual aspect. Theoretical foundations of trash are discussed. Further benefited from historical and social aspect of trash. It is questioned that how do scholars conceptualized the trash, what do they say about it?

Firstly we need to ask what is the source of trash. How is it generated? Secondly \ldots

%%%
%%%
%%%
\section{Throw away culture}
%%% Reference from Identity, mobility and the throwaway society
The term is actually a criticism of over consumption of short-live disposable objects.
\todo[inline]{We live in a throwaway society (Barr, 2004; Cooper, 2003, 2005; Cooper and Mayers, 2000; Strasser, 1999, cf. O’Brien, 1999; Hawkins and Muecke, 2003); (ref from another article)} whose behavioral pattern produce every time and everywhere. Even if conducted a qualitative research people are really do not throw away their things. \paraphrase{The research did not include the leftovers and detritus of food consumption packaging, bottles, and food waste, for example and neither was it concerned with another major category contributor to the volume of household waste, those `disposable' goods that are the primary means to maintaining bodily hygiene and cleanliness (Shove, 2003)}. They analyzed the things like television, furniture and toys like that.

\comment{Continuously consuming things and disposing of something. It is an important concept to understand why trash is trash? (or how it become trash?)}

@@

@@

\comment{zaten zengin olanın atma lüksü var.}

\paraphrase{Life magazine fashionably heralded the advent of the "throwaway society" in 1955. 1971 daniel ingersoll reporting on his findings in the journal man in the notheast, "the industrial revolution ... was supplying the customer with hundreds of disposable containers and materials bt the end of the nineteenth century. the estimated 25.000 cubic yards of fill deposited in the upper portion of puddle dock show that the age of the throw away world began not in the twentieth century but during the nineteenth."} Therefore Industrial age played significant role (engine of the mountains of rubbish.)

@@

@@

\todo{need to elaborate}

@@

I began to save all of my coffee cups to use as "canvases" for making art. Transforms coffee cups that are no longer trash but a vehicle for art, ideas, conversation and memories of a social moment upcycled from the detritus of our throw-away caffeine culture. I like my coffee or tea in a paper take-out cup. Even better than the contents, I like the used cup as a surface on which to draw and paint. And on the bottom of each one, I write the date, location, occasion and beverage consumed so that every hand-made cup artwork becomes the record of a social moment. Each cup representing a daily caffeine break. The installation makes visible largely unconscious patterns of consumption; this is what one simple take-away purchase looks like over the course of three years, this is what would usually be thrown away. It can be seen as a measure of time gone by, of money spent, of space to be taken up in a landfill. But as I upcycle each used cup into an artwork, it becomes the measure of other things as well: an artist's regular habit of generating new ideas, a diary of time spent with friends and colleagues, and the cumulative positive effect of doing something small and manageable every day. There are different versions of it. paintings on paper coffee cups displayed as installation in public window spaces. She publicly draw their cups (the cup art window installation and public drawing project were on view repeated showed at many places and date. During public drawing projects she draw with other people. and so. Buying a beverage is a daily event for Leech (and also many people. These coffee shops all around the world. As she drinks her coffee in the public, she also publicly transform its cup.

@@

Visual artist and graphic designer Ruby Silvious embarked on a quirky, personal experiment, set to last for 363 days. She decided to repurpose soggy and stained tea bags as unconventional, blank canvases, just waiting to be filled with her artistic expression. The project, entitled 363 Days of Tea, allows Silvious to challenge herself by transforming the recycled material with her intricate illustrations—the artist draws, paints, and forms collages on the salvaged tea bags. This project serves as Silvious’ daily journal, allowing her to record her thoughts and feelings by creating wonderful moody and whimsical designs on little teabag papers. Every day she creates a new piece that reflects her impressions in that moment. Currently based in New York, Silvious’ work has been exhibited internationally and she has received awards and recognition for her talents in paper work, print making and now her most recent endeavour of re-purposing recycled and found materials.

@@

@@

@@

% Related with tracy emin, photos of every cast off/discard/reject, understanding human through their discard.
\comment{GARBOLOGY} Garbology is a study of waste as a social science. Applying methodologies of archeology to the human debris. \todo[inline]{reference rubbish archeology of garbage} \paraphrase{"Weberman infamously used techniques of what he deemed garbology to uncover what he saw as the essential nature of people. He once said, perhaps indirectly referencing Jean Brillat-Savarin’s quote about food, “You are what you throw away.”" \cite{lukas2012garbage}}

@@

@@

\paraphrase{Tracey Emin puts her private life to the public. The work, which Emin now describes as a portrait of a young woman. It is a time capsule. The cigarettes that litter the floor will one day no longer exist; neither will the newspapers. Around her there are pieces of junks speared all over the room. We can understand from her junk what type of life her has. We enter the world of artist through the her trashes.} \todo[inline]{Dört günden beri yataktan çıkmamış. İşte o sürede birikenler.}

%%%
%%%
%%%
% FROM Examined Life
\section{Zizek's Approach to Garbage}
(There is a curious fragment where Zizek, dressed as a sanitation man, stands in a waste deposit in a pile of garbage and ponders over garbage and human existence. In documentary film, Examined-life, Zizek talks about ecology in the middle of a garbage dump in London, and his part starts with these sentence: "This---garbage dump--- is where we should start feeling at home". He asserts his claim at first and go through explaining how ecology turns to ideology and mentions wrong perception about the ecology. Draw attention to notion of even if trash disappears from our world but not world. It seems as though the thrown out garbage disappears from our world. However, it disappears only from the world of illusions, but still exists in reality. He thinks that the way of approaching ecology is problematic, because accepting that nature as a balanced harmonious thing. He claims that it is ideological in the sense that wrong thinking important problems. Nature contains unimaginable catastrophes. think oil and distinct animals and plants. we profit balance part of the nature but it is created from catastrophe. Are we aware of this catastrophe. He asserts that ecology will slowly turn to religion that "is a kind of an unquestionable highest authority." Ideology of ecology warns us like, "Don't do that. It would be too much." its voice is like "Don't mess with D.N.A. Don't mess with nature. Don't do it" etc. We should not forget that we are part of the ecology. We must more alienated from the nature. We must find poetry and spirituality in the dimension of trash. That's the true love of world. Love is not about idealization. This part will be extended later.)

% FROM https://commons.wikimedia.org/wiki/File:Albatross_at_Midway_Atoll_Refuge_%288080507529%29.jpg
\begin{figure}[h!]
  \centering
  \includegraphics[height=6cm]{graphics/ChrisJordan-Albatross.jpg}
  \caption{Chris Jordan, Albatross at Midway Atoll Refuge, 2009}
  \label{fig:ChrisJordan_Albatross}
\end{figure}

The unaltered stomach contents of a dead albatross chick photographed on Midway Atoll National Wildlife Refuge in the Pacific in September 2009 include plastic marine debris fed the chick by its parents.

Using spare narration and stunning imagery, Chris Jordan's feature film MIDWAY explores the plight of Laysan albatross plagued by the ingestion of our plastic trash. Both elegy and warning, the film explores the interconnectedness of species, with the albatross on Midway as a mirror of our humanity.

Even if garbage leave outs our life, we do not care about the results of it. And it is captured by the works of Chris Jordan.In this photo series it captures

% Effect of plastic on wildlife in Antartica.
% Her ne kadar biz çöpü attıktan bizim hayatımızdan çıksa da yok olmuyor. Sadece başka bir yerlere gidiyor. Mesela kuşların midelerine. Chris Jordan'ının imageları bunu çok da güzel açığa çıkartıyor. Bizim çöpleriminde habersiz hayvanlar bunları yiyorlar. Bir yandan ürettiğimiz ürünler ile kaynakları tüketirken bir diğer yandan ise artıklarımız diğer yaşanları tüketiyor. Dikkat çekmek istediğim nokta aslında ekolojik hassasiyetlerden çok aslında elimizde avucumuzda ne varsa onları tüketiyor olmamız. Karşı durduğum nokta ise tam olarak burası.

@@

%%%
%%%
%%%
\section{Rubbish Theory}
Objects have a lifetime and they don't remain same through that lifetime. Their value, usage, location change over time. During its lifetime objects may circulate different markets and values systems like economical value, social value, aesthetic value etc. Especially this cycle has picked up speed with the advent of consumer culture, our most recent technological gadgets becoming obsolete within 3 years. Objects function and value are transformed by relocation and revaluation of objects from one place to the other or one discipline to another. This flow(transition) and transformation theorized with Rubbish Theory by Thompson \cite{thompson1979rubbish}. Thompson looks at the creation and destruction of value in man-made objects, cultural artifacts, and ideas. He notes how an object’s economic and/or cultural value diminishes over time rendering the objects worthless or redundant. The theory looks at how some of these objects then regain value, such as antiques or historic homes. It claims that there are three types of objects; transient (normal state, decreasing value, circulating), durable (permanent, increasing value, removed from circulation) and rubbish(zero value, will be destroyed or reinvested for economic and social value). The transition from transient to durable is only possible firstly transient to rubbish and later rubbish to durable. Further, there is a common idea/argument/motto that is "trash to treasure" among artists who use trash as a medium. Rubbish theory presents a conceptual approach to this argument.

>>>>

In this chapter trash and the practice of transforming trash is examined in theoretical and conceptual aspect. Theoretical foundations of trash are discussed. Further benefited from historical and social aspect of trash. It is questioned that how do scholars conceptualized the trash. \comment{(what do they say about it?)} and how artist are approached these notions? and how their work viewed as their offered window or framework.

Firstly we need to ask what is the source of trash. How is it generated? Secondly what are the behaviors behind the producing trash?

%%%
%%%
%%%
\section{Throw away culture}

\todo{throwaway spirit (vance packard)}

excessive use of short-lived/single-use or disposable objects. Disposable items are first introduced X and their usage accelerated after Y. There are Z factors. / reduced cost and qualitative products. Life magazine first introduced the term "throw-away" mentioning that behavioral pattern of society.

disposable: made to be used once or only a few times. made to be thrown away after one use or several uses.

One of the possession that are spreaded to the community is disposable items. They are designed for single-use and personal items. Not reusing of these items are intended.

Even if disposable items are reduces the labour and human resources in a short term they are create mountains of garbage.

They are used very short-time. Their lifetime can be measured in minutes in terms of usage. I have never seen such person that uses own paper cup again and again. However their usage durations are very short, they continue to exist in the nature.

Waste is considered as something useless, something no longer has value; something sufficiently degraded so that the cost of reclaimation seems higher than the cost of disposal, in other words, something unprofitable.

We are very good at producing waste as well as hiding our garbage.

Is it trash or trashed? Is it waste or wasted?

different aspects of our life, eating, drinking, working, traveling, all of them are leave behind wastes and that are become invisible.

we are sorrunded by all kinds of consumer goods [bevarages, ...] We are consing everywhere while walking, working and travelling.

\paraphrase{The value of things rises and diminishes according to the work they do or the feature imagined for them, in other words, to their potential realized in time. Waste by Willian Viley.}

\paraphrase{The strange think about many products that are produced these days is that they are not made to last for a long time. Importantly the term throw away society has a slightly negative connotation, or meaning. When you describe a society as a throw away society, you are probably critising that behaviours or showing your disapproval. }

\begin{itemize}
\item Which trash? Disposable
\item When is it introduced first disposable and how?
\item Terminology?
\item Counter argument.
\end{itemize}

\paraphrase{‘being wasteful in the ways we live is encouraged, expected and in many instances impossible to avoid’ (Hawkins 2006: x) In the late twentieth century, in the context of increasing environmental awareness, this consciousness has altered yet again, and waste has ‘been revalued and recoded from rubbish to recyclable resource, it has moved from the bin to the compost heap, it has insinuated itself into our lives in dif  ferent ways and with dif  ferent ef  fects’ (Hawkins 2006: 5).}

%%% Reference from Identity, mobility and the throwaway society
The term is actually a criticism of over consumption of short-live disposable objects.
\paraphrase{We live in a throwaway society (Barr, 2004; Cooper, 2003, 2005; Cooper and Mayers, 2000; Strasser, 1999, cf. O’Brien, 1999; Hawkins and Muecke, 2003); (ref from another article)} whose behavioral pattern produce every time and everywhere. \todo{ref.} \comment{Scholars argue that contemporary societies are throwaway societies.}

\comment{The term overconsumption refers to a way of living in which the lifestyle patterns of human beings lead to an accelerated expenditure of natural resources.}

@@

Even if conducted a qualitative research people are really do not throw away their things. \paraphrase{The research did not include the leftovers and detritus of food consumption packaging, bottles, and food waste, for example and neither was it concerned with another major category contributor to the volume of household waste, those `disposable' goods that are the primary means to maintaining bodily hygiene and cleanliness (Shove, 2003)}. They analyzed the things like television, furniture and toys like that.

@@

[Social classification, throw away culture, place in society.] \paraphrase{The flip side of this paradigm is that a person's wealth has become measured not only in how much he or she can afford to consume, but in how much he or she can afford to throw away. America is one of the greatest country in terms of generating trash and exporting them to the other third world, fourth world countries.\cite{cerny1996recycled}} \todo{footnote, fourth world countries}

[first occurrence of term.]\paraphrase{Life magazine fashionably heralded the advent of the "throwaway society" in 1955. 1971 daniel ingersoll reporting on his findings in the journal man in the notheast, "the industrial revolution ... was supplying the customer with hundreds of disposable containers and materials bt the end of the nineteenth century. the estimated 25.000 cubic yards of fill deposited in the upper portion of puddle dock show that the age of the throw away world began not in the twentieth century but during the nineteenth."} Therefore Industrial age played significant role (engine of the mountains of rubbish.)

@@

Some of the works of artist can be examined in this pheomena.

@@

%*************************************
% From ontology of trash
% Taken to its obsessive extreme, the germ theory proscribes companionship. The Latin root for this word, cum pani , literally means to share bread. But insofar as each eater harbors untold numbers of hazardous germs, it is safest to keep one’s food strictly to one’s self. Safety in a world of bacteria implies isolation. Packaging successfully isolates both food and consumer within a structure of sterile control. In essence, it encloses the commons. Susan Strasser narrates part of the history of this enclosure through the career of the disposable drinking cup, which appeared in the early years of the twentieth century.

% Susan Strasser
% While the sanitary advantages of toilet paper might have been obvious, those of the paper cup required a belief in germs. The widespread use of paper cups was a direct result of a public health crusade educating people about the invisible organisms spread by the common drinking cups once standard in public places, especially trains and railroad stations. Manufacturers of paper cups teamed up with public health authorities to campaign for federal and state regulations banning common drinking cups from use in interstate traffic. Succeeding in 1912, they competed for the business of the railroads and train stations\ldots
% Disposable paper cups met significant resistance. Most public places offered them in coin-operated dispensers, and some people were not willing to pay for what had once been free. Respectable travellers carried their own cups, available in metal and celluloid in a variety of collapsable and folding designs. Others reused paper cups from the trash or drank out of the public tanks, putting their lips to the faucet or using the cover of the tank as a cup. Some people protested against the vending machines: soldiers smashed paper cup dispensers in Washington’s Union Station during President Wilson’s inauguration in 1913. And some public places installed drinking fountains instead of paper cups dispensers, although at first these, too, were attacked as unsanitary because people could touch the nozzle with their lips.

% The commodities of food and drink must be safe, sterile and private.

% But there are lots of disposable items and single use items. Some of them can seen my project. Each of them have different use and created from different requirement of modern societies. This is not my intention to understand the reasons of disposable items just want to illustrate the notion and give and idea about it.

% Hijyenik mi değil mi bilmiyorum, o benim derdim değil, Başka bir tez konusu, ona çözüm üretmek de derdim değil. Ama sonuçları ile ilgileniyorum.

%....................................

@@

\paraphrase{I began to save all of my coffee cups to use as "canvases" for making art. Transforms coffee cups that are no longer trash but a vehicle for art, ideas, conversation and memories of a social moment upcycled from the detritus of our throw-away caffeine culture. I like my coffee or tea in a paper take-out cup. Even better than the contents, I like the used cup as a surface on which to draw and paint. And on the bottom of each one, I write the date, location, occasion and beverage consumed so that every hand-made cup artwork becomes the record of a social moment. Each cup representing a daily caffeine break. The installation makes visible largely unconscious patterns of consumption; this is what one simple take-away purchase looks like over the course of three years, this is what would usually be thrown away. It can be seen as a measure of time gone by, of money spent, of space to be taken up in a landfill. But as I upcycle each used cup into an artwork, it becomes the measure of other things as well: an artist's regular habit of generating new ideas, a diary of time spent with friends and colleagues, and the cumulative positive effect of doing something small and manageable every day. There are different versions of it. paintings on paper coffee cups displayed as installation in public window spaces. She publicly draw their cups (the cup art window installation and public drawing project were on view repeated showed at many places and date. During public drawing projects she draw with other people. and so. Buying a beverage is a daily event for Leech (and also many people. These coffee shops all around the world. As she drinks her coffee in the public, she also publicly transform its cup.} \todo{cite her website}

inside of glass window. public space. publicly drawing, as she drinks her coffee publicly, also paints them publicly.

@@

\paraphrase{Visual artist and graphic designer Ruby Silvious embarked on a quirky, personal experiment, set to last for 363 days. She decided to repurpose soggy and stained tea bags as unconventional, blank canvases, just waiting to be filled with her artistic expression. The project, entitled 363 Days of Tea, allows Silvious to challenge herself by transforming the recycled material with her intricate illustrations—the artist draws, paints, and forms collages on the salvaged tea bags. This project serves as Silvious’ daily journal, allowing her to record her thoughts and feelings by creating wonderful moody and whimsical designs on little teabag papers. Every day she creates a new piece that reflects her impressions in that moment. endeavour of re-purposing recycled and found materials.} \todo{cite website}

This work is for fathers day. catches the important moments of days and works as a diary.

@@

turns numbers to visuals. provide different way to understand the statistics and the missed reality of consumerism. creates gigantic prints to express numbers in a visual manner.

draws attention the the global consumerism. reveals the reality that is hard to understand. Because it is spread to the community and time.

@@

Trash tells about societies and also reveals personal aspects of peoples life.

What people consume is actually tells many things about them. As scholars mentioned that throughout the discards of someone else many thing can be understand. They are end product of our activities and it can be traced through the discard and garbage.

@@

% Related with tracy emin, photos of every cast off/discard/reject, understanding human through their discard.
\comment{GARBOLOGY} Garbology is a study of waste as a social science. Applying methodologies of archeology to the human debris. \paraphrase{"Weberman infamously used techniques of what he deemed garbology to uncover what he saw as the essential nature of people. He once said, perhaps indirectly referencing Jean Brillat-Savarin’s quote about food, “You are what you throw away.”" \cite{lukas2012garbage}}

@@

% Related with tracy emin, photos of every cast off/discard/reject, understanding human through their discard.
\comment{GARBOLOGY} Garbology is a study of waste as a social science. Applying methodologies of archeology to the human debris. \todo{reference rubbish archeology of garbage} \paraphrase{"Weberman infamously used techniques of what he deemed garbology to uncover what he saw as the essential nature of people. He once said, perhaps indirectly referencing Jean Brillat-Savarin’s quote about food, “You are what you throw away.”" \cite{lukas2012garbage}}

% Garbology, from Encyclopedia, Abhijit Roy
\paraphrase{"The field of garbology involves the study of refuse and waste. It enables researchers to document information on the nature and changing patterns of modern refuse, hence assisting in the study of contemporary human society or culture. According to the Oxford English Dictionary, the term was first used by waste collectors in the 1960s. A. J. Weberman popularized the term in describing his study of Bob Dylan’s garbage in 1970. It was pioneered as an academic discipline by William Rathje at the University of Arizona in 1973."} \todo{reference}

% Rubbish: The Archeology of Garbage, p.24
\paraphrase{As noted, the Garbage Project has now been sorting and evaluating garbage, with scientific rigor, for two decades. The Project has proved durable because its findings have supplied a fresh perspective on what we know---and what we think we know---about certain aspects of our life. (example of Medical researches)} \todo{reference}

\paraphrase{the work of archaeologists such as William Rathje and Cullen Murphy has of  fered significant insights into the relationship between archaeological artefacts and garbage, exploring the function of trash as a resource for understanding cultural and social practice. At the same time, thinkers such as Zygmunt Bauman and Giorgio Agamben have shed light on the fate of   the human being as a wasted or discarded element in discourses of socio-political hygiene. (Trash Culture)}

@@

\paraphrase{Tracey Emin puts her private life to the public. The work, which Emin now describes as a portrait of a young woman. It is a time capsule. The cigarettes that litter the floor will one day no longer exist; neither will the newspapers. Around her there are pieces of junks speared all over the room. We can understand from her junk what type of life her has. We enter the world of artist through the her trashes.} \todo[inline]{Hastalık dönemi falan.}

%%%
%%%
%%%
% FROM Examined Life
\section{Zizek's Approach to Garbage}
Sürekli çöpü kendimizden uzak tutmaya çalışırken aslında zizek bize bunun tam da tersini yapmamızı bize öneriyor. Bu adam aslında insanlar doğaya zarar vermiyorlar demiyor. Onun dediği aslında yanlış sebep sonuç ilişkileri kurduğumuz üzerinden gidiyor.

This section is related with the increasing interest on ecology. globa warming is one of them. These types of news and talks increasingly find a place more and more on media.

trasnforming trash is not related with ecological perspective. We are not trying to save the planet earth or mother nature. Beyond ecological concerns we are trying to find ways to live our trash.

as trash live longer than human being, next generations have to cope with previous generations trash.

(There is a curious fragment where Zizek, dressed as a sanitation man, stands in a waste deposit in a pile of garbage and ponders over garbage and human existence. In documentary film, Examined-life, Zizek talks about ecology in the middle of a garbage dump in London, and his part starts with these sentence: "This---garbage dump--- is where we should start feeling at home". He asserts his claim at first and go through explaining how ecology turns to ideology and mentions wrong perception about the ecology. Draw attention to notion of even if trash disappears from our world but not world. It seems as though the thrown out garbage disappears from our world. However, it disappears only from the world of illusions, but still exists in reality. He thinks that the way of approaching ecology is problematic, because accepting that nature as a balanced harmonious thing. He claims that it is ideological in the sense that wrong thinking important problems. Nature contains unimaginable catastrophes. think oil and distinct animals and plants. we profit balance part of the nature but it is created from catastrophe. Are we aware of this catastrophe. He asserts that ecology will slowly turn to religion that "is a kind of an unquestionable highest authority." Ideology of ecology warns us like, "Don't do that. It would be too much." its voice is like "Don't mess with D.N.A. Don't mess with nature. Don't do it" etc. We should not forget that we are part of the ecology. We must more alienated from the nature. We must find poetry and spirituality in the dimension of trash. That's the true love of world. Love is not about idealization. This part will be extended later.)

@@

%%%
%%%
%%%
\section{Rubbish Theory}

\comment{Çöpün hep çöp gibi kalmadığı ve farklı bakış açıları olabileceğini gördük. Bu hareketlilik ve farklılık ise bir teorik çerçeveye oturulmuş, hadi ona baklım şimdi. }

\paraphrase{Michael Thompson’s 1979 study Rubbish Theory  elaborated an understanding of rubbish as part of a f lexible and shifting system of value construction, underlying notions of innovation, creativity and social status. (Trash Culture)}

\paraphrase{The potential of the discarded thing also relies on its status as a thing approaching a ‘zero point’ of value. In other words, it has reached a point in transition between the world of   the functioning, the useful and visible, and the realm of   the invisible, the non-functioning and empty. As Michael Thompson’s Rubbish Theory  suggests, at its nadir in a cycle of consumption and production, rubbish is both ready for disappearance and yet ripe for reinvestment, reinterpretation or revaluing. (Trash Culture)}

Objects have a lifetime and they don't remain same through that lifetime. Their value, usage, location change over time. During its lifetime objects may circulate different markets and values systems like economical value, social value, aesthetic value etc. Especially this cycle has picked up speed with the advent of consumer culture, our most recent technological gadgets becoming obsolete within 3 years. Objects function and value are transformed by relocation and revaluation of objects from one place to the other or one discipline to another. This flow(transition) and transformation theorized with Rubbish Theory by Thompson \cite{thompson1979rubbish}. Thompson looks at the creation and destruction of value in man-made objects, cultural artifacts, and ideas. He notes how an object’s economic and/or cultural value diminishes over time rendering the objects worthless or redundant. The theory looks at how some of these objects then regain value, such as antiques or historic homes. It claims that there are three types of objects; transient (normal state, decreasing value, circulating), durable (permanent, increasing value, removed from circulation) and rubbish(zero value, will be destroyed or reinvested for economic and social value). The transition from transient to durable is only possible firstly transient to rubbish and later rubbish to durable. Further, there is a common idea/argument/motto that is "trash to treasure" among artists who use trash as a medium. Rubbish theory presents a conceptual approach to this argument.

### 2016-01-17 drafts/chapter4.tex
Relocation, turnitin fixes
Former-commit-id: e8de078896595446f38348c7c970a0b9f22fae30

>>>>

\comment{Post-consumer  paper  waste  has  to  be  manually sorted  into  different  types,  such  as  paperboard, office  paper,  and  newsprint.  Staples  are  removed with  a  magnet.  The  paper  is  chopped  into  small pieces  and  added  to  water  and  chemicals.  Denser objects that are not paper sink. Any inked or colored  papers  must  be  deinked  with  sodium  silicate or  sodium  hydroxide.  Some  paper  pulp  is  also bleached. The effluent of the pulping process, called “sludge,”  includes  chemicals,  inks,  clay  (from glossy paper), plastics, and short paper fibers. This sludge can be toxic and is landfilled or incinerated. When paper is recycled, the fibers break down and become shorter, requiring the input of virgin material. If virgin pulp is not added, the pulp can be used in lower-quality paper products, such as cardboard or newsprint.}

\comment{Traditionally,  newspapers and magazines have been reused as paper for packing;  covering  different  surfaces,  such  as  windows and furniture; and even as toilet paper. }

### 2016-01-17 drafts/chapter4_reduced.tex
Relocation, turnitin fixes
Former-commit-id: e8de078896595446f38348c7c970a0b9f22fae30

\begin{singlespace}
% FROM Wild Art. quote taken from the television series `American Masters', Season 5, Episode 8, John Cage: I have nothing to say and I am saying it (aired on 17 September 1990).
\epigraph{The first question I ask myself when something doesn't seem to be beautiful is why do I think it's not beautiful? And very shortly you discover that there is no reason. If we can conquer that dislike, or begin to like what we did dislike, then the world is more open. That path ---of increasing one's enjoyment of life--- is the path, I think, we all best take: to use art not as self-expression, but as self-alteration; to become more open.}{\hfill---John Cage, \textit{Wild Art}, 2013}
\end{singlespace}

@@

% NEW PART [collecting] 
\subsection{Collecting}
Collecting discarded objects has carried out through the efforts of mine and people around me. Lars Eighner's instructions helped me a lot when collecting objects. He writes that:

@@

% TODO relocate
%Trash is something that is out of sight, out of mind. Paid little attention to them and only catches attention when it is in wrong place. It is an unexpected object for people. Therefore transformation of it can create powerful and surprising effect onto the people.

%\paraphrase{Thompson comments that we only notice rubbish when it is in the wrong place, and highlights the embarrassment and anxiety that mis-placed rubbish, or rubbish which has found its way in to the wrong place can cause ‘Something which has been discarded, but never threatens to intrude, does not worry us at all.’ (1979: 92) but rubbish in the wrong place is ‘emphatically visible and extremely embarrassing’ (1972: 92). Rubbish objects are things that are no longer used or loved or cared for and often no longer seen. Rubbish objects linger on the periphery of our lives, in the back of the drawer, bottom of the wardrobe or cupboard, corner of the garage or garden shed gathering dust. (Summary From Liz Parsons.)}

@@

I followed the methods of Dada poem to mix the papers used inside of the notebooks. I changed their order and direction. 
\cite{tzara1977seven}, gave the following instructions on how \quotes{[t]o make a Dadaist Poem}:

\begin{quote}
Take a newspaper. Take some scissors. Choose from this paper an article the length you want to make your poem. Cut out the article. Next carefully cut out each of the words that make up this article and put them all in a bag. Shake gently. Next take out each cutting one after the other. Copy conscientiously in the order in which they left the bag. The poem will resemble you. And there you are ---an infinitely original author of charming sensibility, even though unappreciated by the vulgar herd.
\end{quote}

>>>>

% Epigraph
\begin{singlespace}
% FROM Wild Art. quote taken from the television series `American Masters', Season 5, Episode 8, John Cage: I have nothing to say and I am saying it (aired on 17 September 1990).
\epigraph{The first question I ask myself when something doesn't seem to be beautiful is why do I think it's not beautiful? And very shortly you discover that there is no reason. If we can conquer that dislike, or begin to like what we did dislike, then the world is more open. That path ---of increasing one's enjoyment of life--- is the path, I think, we all best take: to use art not as self-expression, but as self-alteration; to become more open.}{\hfill---John Cage, \textit{Wild Art}, 2013}
\end{singlespace}

@@

% NEW PART [collecting] 
\subsection{Collecting}
Collecting discarded objects has carried out through the efforts of mine and people around me. Lars Eighner's instructions helped me a lot when collecting objects. He writes that

@@

@@

I followed the methods of Dada poem to mix the papers used inside of the notebooks. I changed their order and direction. 
\cite{tzara1977seven}, gave the following instructions on how \quotes{[t]o make a Dadaist Poem};

\begin{quote}
Take a newspaper. Take some scissors. Choose from this paper an article the length you want to make your poem. Cut out the article. Next carefully cut out each of the words that make up this article and put them all in a bag. Shake gently. Next take out each cutting one after the other. Copy conscientiously in the order in which they left the bag. The poem will resemble you. And there you are--an infinitely original author of       charming sensibility, even though unappreciated by the vulgar herd.
\end{quote}
